The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-05-22 ms/ms.tex
Updates from Overleaf

One such fundamental model development step is parameter sensitivity testing and/or parameter optimization \cite{qian2018}.
Because parameter values are uncertain, evaluating the effect of parameter values on model output is critical to the model development process \cite{hourdin2017,balaji2022}.
When applied systematically, the result is a Parameter Perturbation Ensemble (PPE), alternatively termed a Perturbed Physics Ensemble.
PPEs have played an important role in assessing projection uncertainty in climate models \cite{sanderson2008,hawkins2019,yamazaki2021,peatier2022,tett2022}.
PPEs also form a basis for automated model calibration through, for example, history matching \cite{williamson2013} or Bayesian uncertainty quantification \cite{cleary2021}.
Our goal in this project is to systematize parameter perturbation activity within our modeling framework, and develop the necessary tools and datasets to efficiently test parameter effects across the full suite of land model processes. 
In doing so, we have generated a large PPE, comprising thousands of parameter sensitivity tests.
In this paper we present that dataset, describe how it was produced, and survey some potential applications.

@@

\begin{figure}[h]
\centering
\includegraphics[width=30pc]{../figs/bar.pdf}
\caption{206 parameters were identified and perturbed across the various domains of the land model.}
\label{fig:params}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/violins.png}
\caption{Global annual gross primary production (GPP) and net ecosystem production (NEP) across the PPE within each of our six forcing scenarios. Each point represents a simulation within the PPE. Points are spaced horizontally to minimize overlap.}
\label{fig:violins}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/violins.png}
\caption{Global annual gross primary production (GPP) and net ecosystem production (NEP) across the PPE within each of our six forcing scenarios. Each point represents a simulation within the PPE. Points are spaced horizontally to minimize overlap.}
\label{fig:violins}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=40pc]{../figs/lai_biome.pdf}
\caption{The eight most influential parameters on leaf area index within the CTL2010 ensemble, globally and within three biomes.}
\label{fig:lai}
\end{figure}

>>>>

One such fundamental model development step is parameter sensitivity testing and/or parameter optimization \cite{qian2018}.
Because parameter values are uncertain, evaluating the effect of parameter values on model output is critical to the model development process \cite{hourdin2017,balaji2022}.
When applied systematically, the result is a Parameter Perturbation Ensemble (PPE), alternatively termed a Perturbed Physics Ensemble.
PPEs have played an important role in assessing projection uncertainty in climate models (Booth 2012; ERL, Murphy 2004; Nature) \cite{sanderson2008,hawkins2019,yamazaki2021,peatier2022,tett2022}.
PPEs also form a basis for automated model calibration through, for example, history matching \cite{williamson2013} (Williamson2017; GMD-NEMO calibration; Couvreux2020 JAMES; Hourdin 2020 JAMES) or Bayesian uncertainty quantification \cite{cleary2021}.
Our goal in this project is to systematize parameter perturbation activity within our modeling framework, and develop the necessary tools and datasets to efficiently test parameter effects across the full suite of land model processes. 
In doing so, we have generated a large PPE, comprising thousands of parameter sensitivity tests.
In this paper we present that dataset, describe how it was produced, and survey some potential applications.

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/bar.pdf}
\caption{193 parameters were perturbed across the various domains of the land model.}
\label{fig:params}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/violins.png}
\caption{Global annual gross primary production (GPP) and net ecosystem production (NEP) across the PPE within each of our six forcing scenarios. Markers are drawn for 10 and 0.28 PgC bins for GPP and NEP, respectively. The marker area is proportional to the number of simulations falling in that bin. In each case the ellipse is centered about the default simulation.}
\label{fig:violins}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/variance.pdf}
\caption{needs caption}
\label{fig:violins}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/lai_biome.pdf}
\caption{The eight most influential parameters on leaf area index within the CTL2010 ensemble, globally and within three biomes.}
\label{fig:lai}
\end{figure}
